---
title: "resazurin_analysis"
author: "Samuel Gurr"
date: "2026-03-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# SET WORKING DIRECTORY 
knitr::opts_knit$set(root.dir = "C:/Users/gurrs/Documents/6_Github_repositories/GurrLab/Resazurin_Pacific_oysters/RAnalysis") # Sam's
#knitr::opts_knit$set(root.dir = "C:/Users/samuel.gurr/Documents/Github_repositories/EAD-ASEB-Airradians_Popgen_OA/") # Sam's
```


```{r}
library(readxl)
library(stringr)
library(pracma)
library(ggplot2)
library(ggpubr)
```

```{r}

metadata_counts <- read.csv("Data/metadata_larvae_counts.csv", sep=',')
# View(metadata_counts)

plate_notes <- metadata_counts %>%  dplyr::select(c('PlateID','Well','Note','X')) %>% dplyr::rename(obs_volume = X)

families <- read.csv("Data/YC26-ebv-crosses-broodpops.csv", sep=',') %>% dplyr::rename(Family = cross)
```

```{r call raw file folders}
resaz_72hpf_filenames <- list.files("Data/20260320_72hpf/", pattern = "\\.xlsx$", full.names = TRUE)
resaz_72hpf_filenames

#  [1] "Data/20260320_72hpf/Resaz_plate1_high_T0_260320_131142.xlsx" "Data/20260320_72hpf/Resaz_plate1_high_T1_260320_1424.xlsx"  
#  [3] "Data/20260320_72hpf/Resaz_plate1_high_T2_260320_1529.xlsx"   "Data/20260320_72hpf/Resaz_plate1_high_T3_260320_1640.xlsx"  
#  [5] "Data/20260320_72hpf/Resaz_plate1_high_T4_260320_1747.xlsx"   "Data/20260320_72hpf/Resaz_plate1_low_T0_260320_1328.xlsx"   
#  [7] "Data/20260320_72hpf/Resaz_plate1_low_T1_260320_1436.xlsx"    "Data/20260320_72hpf/Resaz_plate1_low_T2_260320_1542.xlsx"   
#  [9] "Data/20260320_72hpf/Resaz_plate1_low_T3_260320_1649.xlsx"    "Data/20260320_72hpf/Resaz_plate1_low_T4_260320_1758.xlsx"   
# [11] "Data/20260320_72hpf/Resaz_plate2_high_T0_260320_1316.xlsx"   "Data/20260320_72hpf/Resaz_plate2_high_T1_260320_1420.xlsx"  
# [13] "Data/20260320_72hpf/Resaz_plate2_high_T2_260320_1532.xlsx"   "Data/20260320_72hpf/Resaz_plate2_high_T3_260320_1637.xlsx"  
# [15] "Data/20260320_72hpf/Resaz_plate2_high_T4_260320_1743.xlsx"   "Data/20260320_72hpf/Resaz_plate2_low_T0_260320_1331.xlsx"   
# [17] "Data/20260320_72hpf/Resaz_plate2_low_T1_260320_1433.xlsx"    "Data/20260320_72hpf/Resaz_plate2_low_T2_260320_1544.xlsx"   
# [19] "Data/20260320_72hpf/Resaz_plate2_low_T3_260320_1653.xlsx"    "Data/20260320_72hpf/Resaz_plate2_low_T4_260320_1754.xlsx" 


resaz_15dpf_filenames <- list.files("Data/20260401_15dpf/", pattern = "\\.xlsx$", full.names = TRUE)
resaz_15dpf_filenames


resaz_48dpf_filenames <- list.files("Data/20260504_48dpf/", pattern = "\\.xlsx$", full.names = TRUE)
resaz_48dpf_filenames


# Predictibe phenomics temperature ramp at 1C per day with oyster seed 

resaz_seed30C_filenames <- list.files("Data/20260630_30/", pattern = "\\.xlsx$", full.names = TRUE)
resaz_seed30C_filenames

resaz_seed32C_filenames <- list.files("Data/20260704_32/", pattern = "\\.xlsx$", full.names = TRUE)
resaz_seed32C_filenames

resaz_seed34C_filenames <- list.files("Data/20260706_34/", pattern = "\\.xlsx$", full.names = TRUE)
resaz_seed34C_filenames

```


```{r list files in each folder}
# Read each file into a named list
xlsx_list_72hpf <- setNames(
                      lapply(resaz_72hpf_filenames, read_excel),
                      str_remove(basename(resaz_72hpf_filenames), "\\.xlsx$")
             )


xlsx_list_15dpf <- setNames(
                      lapply(resaz_15dpf_filenames, read_excel),
                      str_remove(basename(resaz_15dpf_filenames), "\\.xlsx$")
             )

xlsx_list_48dpf <- setNames(
                      lapply(resaz_48dpf_filenames, read_excel),
                      str_remove(basename(resaz_48dpf_filenames), "\\.xlsx$")
             )

# Predictibe phenomics temperature ramp at 1C per day with oyster seed 

xlsx_list_seed30C <- setNames(
                      lapply(resaz_seed30C_filenames, read_excel),
                      str_remove(basename(resaz_seed30C_filenames), "\\.xlsx$")
             )

xlsx_list_seed32C <- setNames(
                      lapply(resaz_seed32C_filenames, read_excel),
                      str_remove(basename(resaz_seed32C_filenames), "\\.xlsx$")
             )

xlsx_list_seed34C <- setNames(
                      lapply(resaz_seed34C_filenames, read_excel),
                      str_remove(basename(resaz_seed34C_filenames), "\\.xlsx$")
             )
```

```{r function to convert to dataframe}
covert_to_df <- function (file_in) {
                          file_out <- as.data.frame(file_in[-c(1:26), -c(1,15)]) # drop first columns and first 26 rows
                          colnames(file_out) <- c("Plate_row", 1,2,3,4,5,6,7,8,9,10,11,12)
                          
                          file_out <- file_out %>%  
                              tidyr::pivot_longer(
                                cols = -Plate_row,
                                names_to = "Plate_col",
                                values_to = "flourescence"
                              ) %>% 
                            # dplyr::mutate(filename = x.2) %>% 
                            dplyr::mutate(timepoint = "T0", 
                                          plate = "1", 
                                          Well = paste0(Plate_row,Plate_col),
                                          time= as.POSIXlt((strptime(1311, format = "%H%M")),
                                                           format = "%H:%M")
                                                                                                 
                                          )
                          
                          return(file_out)
                        }

covert_to_df_Gladys <- function (file_in) {
                          file_out <- as.data.frame(file_in[-c(1:26), -c(1,15)]) # drop first columns and first 26 rows
                          colnames(file_out) <- c("Plate_row", 1,2,3,4,5,6,7,8,9,10,11,12)
                          
                          x.hrmin <- as.numeric(gsub("^.*_(\\d+)\\.xlsx$", "\\1", x))
                          file_out <- file_out %>%  
                              tidyr::pivot_longer(
                                cols = -Plate_row,
                                names_to = "Plate_col",
                                values_to = "flourescence"
                              ) %>% 
                            dplyr::mutate(filename = as.character(x.2)) %>% 
                            dplyr::mutate(timepoint = gsub("^.*?(T\\d+).*$", "\\1", x.2), 
                                          plate = gsub("^.*plate(\\d+).*", "\\1", x.2), 
                                          Well = paste0(Plate_row,Plate_col),
                                          time= as.POSIXlt((strptime(x.hrmin, format = "%H%M")),
                                                           format = "%H:%M")
                                                                                                 
                                          )
                          
                          return(file_out)
}


covert_to_df_Gladys <- function (file_in) {
                          file_out <- as.data.frame(file_in[-c(1:26), -c(1,15)]) # drop first columns and first 26 rows
                          colnames(file_out) <- c("Plate_row", 1,2,3,4,5,6,7,8,9,10,11,12)
                          
                          x.hrmin <- as.numeric(gsub("^.*_(\\d+)\\.xlsx$", "\\1", x))
                          file_out <- file_out %>%  
                              tidyr::pivot_longer(
                                cols = -Plate_row,
                                names_to = "Plate_col",
                                values_to = "flourescence"
                              ) %>% 
                            dplyr::mutate(filename = as.character(x.2)) %>% 
                            dplyr::mutate(timepoint = gsub("^.*?(T\\d+).*$", "\\1", x.2), 
                                          plate = gsub("^.*plate(\\d+).*", "\\1", x.2), 
                                          Well = paste0(Plate_row,Plate_col),
                                          time= as.POSIXlt((strptime(x.hrmin, format = "%H%M")),
                                                           format = "%H:%M")
                                                                                                 
                                          )
                          
                          return(file_out)
                        }
covert_to_df_Tecan <- function (file_in) {
  
                          # testing
                          # file_in <- xlsx_list_seed30C[[x.2]]
                          file_out <- as.data.frame(file_in[-c(1:43, 52:55),]) # drop first columns and first 26 rows
                          colnames(file_out) <- c("Plate_row", 1,2,3,4,5,6,7,8,9,10,11,12)
                          
                          x.hrmin <- gsub(".*_(\\d{8})_(\\d{4})_.*", 
                                                     "\\1 \\2",
                                                     x)
                          file_out <- file_out %>%  
                              tidyr::pivot_longer(
                                cols = -Plate_row,
                                names_to = "Plate_col",
                                values_to = "flourescence"
                              ) %>% 
                            dplyr::mutate(filename = as.character(x.2)) %>% 
                            dplyr::mutate(timepoint = gsub("^.*?(T\\d+).*$", "\\1", x.2), 
                                          plate = gsub("^.*plate(\\d+).*", "\\1", x.2), 
                                          Well = paste0(Plate_row,Plate_col),
                                          time= as.POSIXlt((strptime(x.hrmin, format = "%d%m%Y %H%M")),
                                                           format = "%H:%M")
                                                                                                 
                                          )
                          
                          return(file_out)
                        }
```

```{r 72 hpf convert to dataframe}

loop.df           <- data.frame(matrix(nrow = 1, ncol = 8)) # create dataframe to save cumunalitively during for loop
colnames(loop.df) <- c('filename', 'time', 'timepoint', 'Plate_row', 'Plate_col', 'Well', 'plate', 'flourescence') # names for columns in the for loop
rbind.df          <- data.frame() # start dataframe 
for (i in 1:length(resaz_72hpf_filenames)) {
  
 x         <- (basename(resaz_72hpf_filenames[i]))
 x.2       <- sub("\\.xlsx$", "", noquote(x))
 loop.df   <- covert_to_df_2(xlsx_list_72hpf[[x.2]])
 
 rbind.df <- rbind(rbind.df,
                     loop.df) #bind to a cumulative list dataframe
 print(rbind.df) # print to monitor progress
  
}


rbind.df_72hpf <- rbind.df %>% 
                    dplyr::mutate(Date = 20260320,
                                  Treatment = dplyr::case_when(gsub("^(?:[^_]*_){2}([^_]*).*", "\\1",filename) == "low" ~ "26C",
                                                        gsub("^(?:[^_]*_){2}([^_]*).*", "\\1",filename) == "high" ~ "38C"),
                                  PlateID = gsub("^[^_]+_([^_]+_[^_]+)_.*", "\\1", filename))

data_merged_72hpf <- dplyr::left_join(rbind.df_72hpf,metadata_counts, by=c('Date','PlateID', 'Well', 'Plate_row', 'Treatment'))

```

```{r 15 dpf convert to dataframe}
loop.df           <- data.frame(matrix(nrow = 1, ncol = 8)) # create dataframe to save cumunalitively during for loop
colnames(loop.df) <- c('filename', 'time', 'timepoint', 'Plate_row', 'Plate_col', 'Well', 'plate', 'flourescence') # names for columns in the for loop
rbind.df          <- data.frame() # start dataframe 
for (i in 1:length(resaz_15dpf_filenames)) {
  
 x         <- (basename(resaz_15dpf_filenames[i]))
 x.2       <- sub("\\.xlsx$", "", noquote(x))
 loop.df   <- covert_to_df_2(xlsx_list_15dpf[[x.2]])
 
 rbind.df <- rbind(rbind.df,
                     loop.df) #bind to a cumulative list dataframe
 print(rbind.df) # print to monitor progress
  
}


rbind.df_15dpf <- rbind.df %>% 
                    dplyr::mutate(Date = 20260401,
                                  Treatment = dplyr::case_when(plate == 1 ~ "26C",
                                                        plate == 2 ~ "30C",
                                                        plate == 3 ~ "34C",
                                                        plate == 4 ~ "38C"),
                                  PlateID = dplyr::case_when(plate == 1 ~ "plate_1_26",
                                                        plate == 2 ~ "plate_2_30",
                                                        plate == 3 ~ "plate_3_34",
                                                        plate == 4 ~ "plate_4_38"))
rbind.df_15dpf$time
data_merged_15dpf <- dplyr::left_join(rbind.df_15dpf,metadata_counts, by=c('Date','PlateID', 'Well', 'Plate_row', 'Treatment'))

```

```{r 48 dpf convert to dataframe}
loop.df           <- data.frame(matrix(nrow = 1, ncol = 8)) # create dataframe to save cumunalitively during for loop
colnames(loop.df) <- c('filename', 'time', 'timepoint', 'Plate_row', 'Plate_col', 'Well', 'plate', 'flourescence') # names for columns in the for loop
rbind.df          <- data.frame() # start dataframe 
for (i in 1:length(resaz_48dpf_filenames)) {
  
 x         <- (basename(resaz_48dpf_filenames[i]))
 x.2       <- sub("\\.xlsx$", "", noquote(x))
 loop.df   <- covert_to_df_2(xlsx_list_48dpf[[x.2]])
 
 rbind.df <- rbind(rbind.df,
                     loop.df) #bind to a cumulative list dataframe
 print(rbind.df) # print to monitor progress
  
}


rbind.df_48dpf <- rbind.df %>% # note, the names of the files differ from the previous time;oint, so made adjustments here
                    dplyr::mutate(Date = 20260504,
                                  Treatment = dplyr::case_when(
                                                        grepl("26C", plate, ignore.case = TRUE) ~ "26C", # I assumed plates 1-4 are in line with temp, checl with Anna
                                                        grepl("30C", plate, ignore.case = TRUE) ~ "30C",
                                                        grepl("34C", plate, ignore.case = TRUE) ~ "34C",
                                                        grepl("38C", plate, ignore.case = TRUE) ~ "38C"),
                                  PlateID = dplyr::case_when(
                                                        grepl("26C", plate, ignore.case = TRUE) ~ "plate_1_26",
                                                        grepl("30C", plate, ignore.case = TRUE) ~ "plate_2_30",
                                                        grepl("34C", plate, ignore.case = TRUE) ~"plate_3_34",
                                                        grepl("38C", plate, ignore.case = TRUE) ~ "plate_4_38"))



data_merged_48dpf <- dplyr::left_join(rbind.df_48dpf,metadata_counts, by=c('Date','PlateID', 'Well', 'Plate_row', 'Treatment'))


```

```{r seed at 30C convert to dataframe}
loop.df           <- data.frame(matrix(nrow = 1, ncol = 8)) # create dataframe to save cumunalitively during for loop
colnames(loop.df) <- c('filename', 'time', 'timepoint', 'Plate_row', 'Plate_col', 'Well', 'plate', 'flourescence') # names for columns in the for loop
rbind.df          <- data.frame() # start dataframe 
for (i in 1:length(resaz_seed30C_filenames)) {
  
 x         <- (basename(resaz_seed30C_filenames[i]))
 x.2       <- sub("\\.xlsx$", "", noquote(x))
 loop.df   <- covert_to_df_Tecan(xlsx_list_seed30C[[x.2]])
 
 rbind.df <- rbind(rbind.df,
                     loop.df) #bind to a cumulative list dataframe
 print(rbind.df) # print to monitor progress
  
}

# omit rows where flourescnece is NA (nore: this is in all rows 'H')
rbind.df <- rbind.df[!is.na(rbind.df$flourescence), ]
nrow(rbind.df) # 1008


rbind.df_seed30C <- rbind.df %>% # note, the names of the files differ from the previous time;oint, so made adjustments here
                    dplyr::mutate(Date = 20260702,
                                  gain = dplyr::case_when(
                                                        grepl("g65", plate, ignore.case = TRUE) ~ 65, # plates were manually set to a gain at 65 and 70 for all runs
                                                        grepl("g70", plate, ignore.case = TRUE) ~ 70),
                                  PlateID = dplyr::case_when(
                                                             grepl("30_T0", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T0_30C_65g",
                                                             
                                                             grepl("30_T0", filename, fixed = TRUE) &
                                                               grepl("g70",  filename, fixed = TRUE) ~ "T0_30C_70g",
                                                             
                                                             grepl("30_T1", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T1_30C_65g",
                                                             
                                                             grepl("30_T1", filename, fixed = TRUE) &
                                                               grepl("g70",  filename, fixed = TRUE) ~ "T1_30C_70g",
                                                             
                                                             grepl("30_T2", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T2_30C_65g",
                                                             
                                                             grepl("30_T2", filename, fixed = TRUE) &
                                                               grepl("g70",  filename, fixed = TRUE) ~ "T2_30C_70g",
                                                             
                                                             grepl("30_T3", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T3_30C_65g",
                                                             
                                                             grepl("30_T3", filename, fixed = TRUE) &
                                                               grepl("g70",  filename, fixed = TRUE) ~ "T3_30C_70g",
                                                             
                                                             grepl("30_T4", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T4_30C_65g",
                                                             
                                                             grepl("30_T4", filename, fixed = TRUE) &
                                                               grepl("g70",  filename, fixed = TRUE) ~ "T4_30C_70g",
                                                             
                                                             grepl("30_T5", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T5_30C_65g",
                                                             
                                                             grepl("30_T5", filename, fixed = TRUE) &
                                                               grepl("g70",  filename, fixed = TRUE) ~ "T5_30C_70g"))



# metadata not yet ready!
# data_merged_seed30C <- dplyr::left_join(rbind.df_seed30C, <INSERT METADATA>, by=c('Date','PlateID', 'Well', 'Plate_row', 'Treatment'))


```


```{r seed at 34C convert to dataframe}
loop.df           <- data.frame(matrix(nrow = 1, ncol = 8)) # create dataframe to save cumunalitively during for loop
colnames(loop.df) <- c('filename', 'time', 'timepoint', 'Plate_row', 'Plate_col', 'Well', 'plate', 'flourescence') # names for columns in the for loop
rbind.df          <- data.frame() # start dataframe 
for (i in 1:length(resaz_seed34C_filenames)) {
  
 x         <- (basename(resaz_seed34C_filenames[i]))
 x.2       <- sub("\\.xlsx$", "", noquote(x))
 loop.df   <- covert_to_df_Tecan(xlsx_list_seed34C[[x.2]])
 
 rbind.df <- rbind(rbind.df,
                     loop.df) #bind to a cumulative list dataframe
 print(rbind.df) # print to monitor progress
  
}

# omit rows where flourescnece is NA (nore: this is in all rows 'H')
rbind.df <- rbind.df[!is.na(rbind.df$flourescence), ]
nrow(rbind.df) # 1008


rbind.df_seed34C <- rbind.df %>% # note, the names of the files differ from the previous time;oint, so made adjustments here
                    dplyr::mutate(Date = 20260706,
                                  gain = dplyr::case_when(
                                                        grepl("g60", plate, ignore.case = TRUE) ~ 60, # plates were manually set to a gain at 65 and 70 for all runs
                                                        grepl("g65", plate, ignore.case = TRUE) ~ 65),
                                  PlateID = dplyr::case_when(
                                                             grepl("34_T0", filename, fixed = TRUE) &
                                                               grepl("g60",  filename, fixed = TRUE) ~ "T0_34C_60g",
                                                             
                                                             grepl("34_T0", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T0_34C_65g",
                                                             
                                                             grepl("34_T1", filename, fixed = TRUE) &
                                                               grepl("g60",  filename, fixed = TRUE) ~ "T1_34C_60g",
                                                             
                                                             grepl("34_T1", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T1_34C_65g",
                                                             
                                                             grepl("34_T2", filename, fixed = TRUE) &
                                                               grepl("g60",  filename, fixed = TRUE) ~ "T2_34C_60g",
                                                             
                                                             grepl("34_T2", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T2_34C_65g",
                                                             
                                                             grepl("34_T3", filename, fixed = TRUE) &
                                                               grepl("g60",  filename, fixed = TRUE) ~ "T3_34C_60g",
                                                             
                                                             grepl("34_T3", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T3_34C_65g",
                                                             
                                                             grepl("34_T4", filename, fixed = TRUE) &
                                                               grepl("g60",  filename, fixed = TRUE) ~ "T4_34C_60g",
                                                             
                                                             grepl("34_T4", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T4_34C_65g",
                                                             
                                                             grepl("34_T5", filename, fixed = TRUE) &
                                                               grepl("g60",  filename, fixed = TRUE) ~ "T5_34C_60g",
                                                             
                                                             grepl("34_T5", filename, fixed = TRUE) &
                                                               grepl("g65",  filename, fixed = TRUE) ~ "T5_34C_65g"))


# metadata not yet ready!
# data_merged_seed34C <- dplyr::left_join(rbind.df_seed34C, <INSERT METADATA>, by=c('Date','PlateID', 'Well', 'Plate_row', 'Treatment'))


```





Note: call specific df
  * loop.df_m and loop.df_i = columns in **rbind.df_14dpf**
  * plate_id == rows in **data_merged_14dpf** by common plate ID between **rbind.df_14dpf** 
```{r 14 dpf auc calc function}

output.df <- data.frame()
loop.df_m   <- data.frame(unique(rbind.df_15dpf$PlateID)) # call specific df
loop.df_i   <- data.frame(unique(rbind.df_15dpf$Well))  # call specific df


# Call the cumulative dataframe that we will write to in the for loop below
output.cumulative.df <- data.frame() # start dataframe 
output.df            <- data.frame() # start dataframe 
output.cor.df        <- data.frame() # start dataframe 
running.df           <- data.frame(matrix(nrow = 1, ncol = 9)) # create dataframe to save cumunalitively during for loop
colnames(running.df) <- c('Date', 'Treatment', 'PlateID', 'Age', 'Well', 'Family', 'Type', 'Count', 'AUC') # names for columns in the for loop

for(m in 1:nrow(loop.df_m)){
  plate_id      <- data_merged_15dpf %>%   # call specific df
                                dplyr::filter(PlateID %in% loop.df_m[m,1])
for(i in 1:nrow(loop.df_i)){
  well.over.time       <- plate_id %>% 
                                dplyr::filter(Well %in% loop.df_i[i,1]) %>% 
                                dplyr::arrange(time) %>% 
                                dplyr::mutate(hours = as.numeric(difftime(time, 
                                                                          time[1], 
                                                                          units = "hours")),
                                              delta_florescence = flourescence - flourescence[1],
                                              AUC = pracma::trapz(
                                                                  hours, 
                                                                  flourescence)) %>% 
                                dplyr::select('Date', 'Treatment', 'PlateID', 'Age', 'time', 'Family', 'hours',
                                              'Well', 'Type', 'Count', 'AUC', 'delta_florescence')
                      
  output.cumulative.df <- rbind(output.cumulative.df, well.over.time)
  
  running.df$Date      <- well.over.time$Date[1]
  running.df$Treatment <- well.over.time$Treatment[1]
  running.df$PlateID   <- well.over.time$PlateID[1]
  running.df$Age       <- well.over.time$Age[1]
  running.df$Well      <- well.over.time$Well[1]
  running.df$Family    <- well.over.time$Family[1]
  running.df$Type      <- well.over.time$Type[1]
  running.df$Count     <- well.over.time$Count[1]
  running.df$AUC       <- well.over.time$AUC[1]
  
   output.df <- rbind(output.df,
                     running.df) #bind to a cumulative list dataframe
   print(output.df) # print to monitor progress
   
   # mean blank AUC by each plate
  mean.AUC.blanks <- mean(
                           (output.df %>% dplyr::filter(Type %in% 'Blank'))$AUC
                          )
   
} # wells within plate end

}

blanks_meanAUC <- Rmisc::summarySE(
                                  data = (output.df %>% dplyr::filter(Type %in% 'Blank')),
                                  measurevar = 'AUC',
                                  groupvars  = 'PlateID') %>% 
                  dplyr::select(PlateID, AUC) %>% 
                  dplyr::rename(blanks_meanAUC = AUC)


output.cor.df <- merge(output.df, blanks_meanAUC) %>% 
                            dplyr::filter(!Type %in% 'Blank') %>% # omit blanks
                            dplyr::mutate(AUC_cor = AUC-blanks_meanAUC,
                                          # AUC_cor_norm = AUC_cor/Count)
                                          AUC_cor_norm = dplyr::case_when(
                                                                          (AUC_cor < 0 | Count == 0) ~ NA,
                                                                          (AUC_cor > 0 & Count > 0) ~ AUC_cor/Count)) #%>% 
                            #na.omit()
   
   
output.cor.df_final <- merge(plate_notes, output.cor.df) %>% 
                                                dplyr::mutate(Family_EBV = 
                                                   dplyr::case_when(Family > 50 ~ 'Low',
                                                              Family < 20 ~ 'High'))

output.cor.df_final_EBV <- merge(output.cor.df_final, families, by = "Family")


output.cor.df_final_omit <- output.cor.df_final_EBV %>% 
                                dplyr::filter(!obs_volume %in% 'has no volume') #%>% 
                                #dplyr::filter(!Count < 10)


delta_abs_figure <- ggplot(
          (output.cumulative.df %>% dplyr::filter(!(Type == 'Sample' & Count == 0))),
           aes(hours, delta_florescence, group = Well)) +
      # geom_point(aes(color = Type)) +
      geom_smooth(aes(color = Type), method = "lm", se = FALSE) +
  facet_wrap(~Treatment,scales = "free")
delta_abs_figure


AUC_cor_by_count <- ggplot(output.cor.df_final_omit, 
                aes(x = Count, y = AUC_cor,  color = Family_EBV)) +
  geom_point(fill = "steelblue")+
  facet_wrap(~Treatment,scales = "free")
AUC_cor_by_count

summary.df <- Rmisc::summarySE(
                      data = (output.cor.df),
                      groupvars = c('Family', 'Treatment'),
                      measurevar = 'AUC_cor_norm')

summary.df_EBV <- merge(summary.df, families, by = "Family") %>% 
                  dplyr::mutate(dam_sire_pop = paste0(dam_pop,"_", sire_pop))

summary.df_EBV <- summary.df_EBV %>% dplyr::mutate(Family_EBV = 
                                                   dplyr::case_when(Family > 50 ~ 'Low',
                                                              Family < 20 ~ 'High'))

AUC_cor_by_count_fam <- ggplot(summary.df_EBV, 
                aes(x = as.factor(as.numeric(Family)), y = AUC_cor_norm, color = Family_EBV)) +
  geom_point(fill = "steelblue") +
  geom_errorbar(aes(ymin = AUC_cor_norm - se, ymax = AUC_cor_norm + se), width = 0.2) +
  theme_classic() +
  facet_wrap(~Treatment,scales = "free")

AUC_cor_by_EBV <- ggplot(summary.df_EBV, 
                aes(x = ebv_mpv, y = AUC_cor_norm, color = Family_EBV)) +
  geom_point(fill = "steelblue") +
  geom_errorbar(aes(ymin = AUC_cor_norm - se, ymax = AUC_cor_norm + se), width = 0.02) +
  theme_classic() +
  facet_wrap(~Treatment,scales = "free")

AUC_cor_by_DamSire <- ggplot(summary.df_EBV, 
                aes(x = ebv_mpv, y = AUC_cor_norm, color = dam_sire_pop)) +
  geom_point(fill = "steelblue") +
  geom_errorbar(aes(ymin = AUC_cor_norm - se, ymax = AUC_cor_norm + se), width = 0.02) +
  theme_classic() +
  facet_wrap(~Treatment,scales = "free")

AUC_cor_by_count_fam <- ggplot(summary.df_EBV, 
                aes(x = Treatment, y = AUC_cor_norm, 
                    group = as.factor(as.numeric(Family)), 
                    color = dam_sire_pop)) +
  geom_point(fill = "steelblue") +
  geom_smooth(method = "loess", se = TRUE) +
  # geom_errorbar(aes(ymin = AUC_cor_norm - se, ymax = AUC_cor_norm + se), width = 0.2) +
  theme_classic() + 
  facet_wrap(~Family_EBV)


AUC_cor_by_count_fam2 <- ggplot(summary.df_EBV, 
                aes(x = Treatment, y = AUC_cor_norm, group = Family_EBV, color = dam_sire_pop)) +
  geom_point(fill = "steelblue") +
  geom_smooth(method = "loess",               # Apply LOESS smoothing
              se = TRUE,                      # Show 95% CI (grey ribbon)
              level = 0.95,
              span = 0.8)  +
  theme_classic() + 
  facet_wrap(~Family_EBV)



# ?facet_wrap
ggarrange(delta_abs_figure,
          AUC_cor_by_count,
          AUC_cor_by_count_fam,
          AUC_cor_by_count_fam2,
          nrow=2,
          ncol=2)

ggarrange(
          AUC_cor_by_count_fam,
          AUC_cor_by_count_fam2,
          nrow=2,
          ncol=1)

pdf("Output/20260401_resazurin.pdf", height = 6, width = 6)
ggarrange(
          AUC_cor_by_count_fam,
          AUC_cor_by_count_fam2,
          nrow=2,
          ncol=1)
dev.off()

```



Note: call specific df
  * loop.df_m and loop.df_i = columns in **rbind.df_48dpf**
  * plate_id == rows in **data_merged_48dpf** by common plate ID between **rbind.df_48dpf** 
```{r 48 dpf auc calc function}

output.df   <- data.frame()
loop.df_m   <- data.frame(unique(rbind.df_48dpf$PlateID))  # call specific df
loop.df_i   <- data.frame(unique(rbind.df_48dpf$Well))  # call specific df

# Call the cumulative dataframe that we will write to in the for loop below
output.cumulative.df <- data.frame() # start dataframe 
output.cor.df        <- data.frame() # start dataframe 
output.cor.df_final  <- data.frame() # start dataframe 
running.df           <- data.frame(matrix(nrow = 1, ncol = 9)) # create dataframe to save cumunalitively during for loop
colnames(running.df) <- c('Date', 'Treatment', 'PlateID', 'Age', 'Well', 'Family', 'Type', 'Count', 'AUC') # names for columns in the for loop

for(m in 1:nrow(loop.df_m)){
  plate_id      <- data_merged_48dpf %>%   # call specific df
                                dplyr::filter(PlateID %in% loop.df_m[m,1])
for(i in 1:nrow(loop.df_i)){
  well.over.time       <- plate_id %>% 
                                dplyr::filter(Well %in% loop.df_i[i,1]) %>% 
                                dplyr::arrange(time) %>% 
                                dplyr::mutate(hours = as.numeric(difftime(time, 
                                                                          time[1], 
                                                                          units = "hours")),
                                              delta_florescence = flourescence - flourescence[1],
                                              AUC = pracma::trapz(
                                                                  hours, 
                                                                  flourescence)) %>% 
                                dplyr::select('Date', 'Treatment', 'PlateID', 'Age', 'time', 'Family', 'hours',
                                              'Well', 'Type', 'Count', 'AUC', 'delta_florescence')
                      
  output.cumulative.df <- rbind(output.cumulative.df, 
                                well.over.time)
  
  running.df$Date      <- well.over.time$Date[1]
  running.df$Treatment <- well.over.time$Treatment[1]
  running.df$PlateID   <- well.over.time$PlateID[1]
  running.df$Age       <- well.over.time$Age[1]
  running.df$Well      <- well.over.time$Well[1]
  running.df$Family    <- well.over.time$Family[1]
  running.df$Type      <- well.over.time$Type[1]
  running.df$Count     <- well.over.time$Count[1]
  running.df$AUC       <- well.over.time$AUC[1]
  
   output.df <- rbind(output.df,
                     running.df) #bind to a cumulative list dataframe
   print(output.df) # print to monitor progress
   
   # mean blank AUC by each plate
  mean.AUC.blanks <- mean(
                           (output.df %>% dplyr::filter(Type %in% 'Blank'))$AUC
                          )
   
} # wells within plate end

}

blanks_meanAUC <- Rmisc::summarySE(
                                  data = (output.df %>% dplyr::filter(Type %in% 'Blank')),
                                  measurevar = 'AUC',
                                  groupvars  = 'PlateID') %>% 
                  dplyr::select(PlateID, AUC) %>% 
                  dplyr::rename(blanks_meanAUC = AUC)


output.cor.df <- merge(output.df, blanks_meanAUC) %>% 
                            dplyr::filter(!Type %in% 'Blank') %>% # omit blanks
                            dplyr::mutate(AUC_cor = AUC-blanks_meanAUC,
                                          # AUC_cor_norm = AUC_cor/Count)
                                          AUC_cor_norm = dplyr::case_when(
                                                                          (AUC_cor < 0 | Count == 0) ~ NA,
                                                                          (AUC_cor > 0 & Count > 0) ~
                                                                            AUC_cor/Count)) #%>% 
                            #na.omit()
   

# 
# output.cor.df_final <- merge(plate_notes, output.cor.df) %>% 
#                                                 dplyr::mutate(Family_EBV = 
#                                                    dplyr::case_when(Family > 50 ~ 'Low',
#                                                               Family < 20 ~ 'High'))
# 
# output.cumulative.df <- merge(plate_notes, output.cumulative.df) %>% dplyr::mutate(Family_EBV = 
#                                                    dplyr::case_when(Family > 50 ~ 'Low',
#                                                               Family < 20 ~ 'High'))



output.cor.df_final_omit <- output.cor.df_final %>% 
                                dplyr::filter(!obs_volume %in% 'has no volume') #%>% 
                                #dplyr::filter(!Count < 10)

output.cumulative.df_omit <- output.cumulative.df %>% 
                                dplyr::filter(!obs_volume %in% 'has no volume') #%>% 
                                #dplyr::filter(!Count < 10)

delta_abs_figure <- ggplot(
          (output.cumulative.df), #%>% dplyr::filter(!(Type == 'Sample' & Count == 0))),
           aes(hours, delta_florescence, group = Well)) +
      # geom_point(aes(color = Type)) +
      geom_smooth(aes(color = Type), method = "lm", se = FALSE) +
  facet_wrap(~Treatment,scales = "free")
delta_abs_figure


AUC_cor_by_count <- ggplot(output.cor.df_final_omit, 
                aes(x = Count, y = AUC_cor,  color = Family_EBV)) +
  geom_point(fill = "steelblue")+
  facet_wrap(~Treatment,scales = "free")
AUC_cor_by_count

summary.df <- Rmisc::summarySE(
                      data = (output.cor.df),
                      groupvars = c('Family', 'Treatment'),
                      measurevar = 'AUC_cor')

summary.df_EBV <- merge(summary.df, families, by = "Family") %>% 
                  dplyr::mutate(dam_sire_pop = paste0(dam_pop,"_", sire_pop))

summary.df_EBV <- summary.df_EBV %>% dplyr::mutate(Family_EBV = 
                                                   dplyr::case_when(Family > 50 ~ 'Low',
                                                              Family < 20 ~ 'High'))

AUC_cor_by_count_fam <- ggplot(summary.df_EBV, 
                aes(x = as.factor(as.numeric(Family)), y = AUC_cor, color = Family_EBV)) +
  geom_point(fill = "steelblue") +
  geom_errorbar(aes(ymin = AUC_cor - se, ymax = AUC_cor + se), width = 0.2) +
  theme_classic() +
  facet_wrap(~Treatment,scales = "free")


AUC_cor_by_EBV <- ggplot(summary.df_EBV, 
                aes(x = ebv_mpv, y = AUC_cor, color = Family_EBV)) +
  geom_point(fill = "steelblue") +
  geom_errorbar(aes(ymin = AUC_cor - se, ymax = AUC_cor + se), width = 0.02) +
  theme_classic() +
  facet_wrap(~Treatment,scales = "free")

AUC_cor_by_DamSire <- ggplot(summary.df_EBV, 
                aes(x = ebv_mpv, y = AUC_cor, color = dam_sire_pop)) +
  geom_point(fill = "steelblue") +
  geom_errorbar(aes(ymin = AUC_cor - se, ymax = AUC_cor + se), width = 0.02) +
  theme_classic() +
  facet_wrap(~Treatment,scales = "free")

AUC_cor_by_DamSire <- ggplot(summary.df_EBV, 
                aes(x =Treatment, y = AUC_cor, 
                    group = as.factor(ebv_mpv),
                    color = as.factor(ebv_mpv))) +
  geom_point(fill = "steelblue") +
  geom_smooth()+
  geom_errorbar(aes(ymin = AUC_cor - se, ymax = AUC_cor + se), width = 0.02) +
  theme_classic() +
  facet_wrap(~Family_EBV)
AUC_cor_by_DamSire

# ?facet_wrap
ggarrange(delta_abs_figure,
          AUC_cor_by_count,
          AUC_cor_by_count_fam,
          AUC_cor_by_count_fam2,
          nrow=2,
          ncol=2)

ggarrange(
          AUC_cor_by_count_fam,
          AUC_cor_by_count_fam2,
          nrow=2,
          ncol=1)

pdf("Output/20260401_resazurin.pdf", height = 6, width = 6)
ggarrange(
          AUC_cor_by_count_fam,
          AUC_cor_by_count_fam2,
          nrow=2,
          ncol=1)
dev.off()

```



Note: call specific df
  * loop.df_m and loop.df_i = columns in **rbind.df_seed34C**
  * plate_id == rows in **data_merged_seed34C** by common plate ID between **rbind.df_seed34C** 
```{r seed 30C auc calc function}

output.df   <- data.frame()
loop.df_m   <- data.frame(unique(rbind.df_seed30C$gain))  # call specific df
loop.df_i   <- data.frame(unique(rbind.df_seed30C$Well))  # call specific df

# Call the cumulative dataframe that we will write to in the for loop below
output.cumulative.df <- data.frame() # start dataframe 
output.cor.df        <- data.frame() # start dataframe 
output.cor.df_final  <- data.frame() # start dataframe 
running.df           <- data.frame(matrix(nrow = 1, ncol = 10)) # create dataframe to save cumunalitively during for loop
colnames(running.df) <- c('Date', 'Treatment', 'PlateID', 'Age', 'Well', 'Family', 'Type', 'Count', 'AUC', 'gain') # names for columns in the for loop

for(m in 1:nrow(loop.df_m)){
  plate_id      <- rbind.df_seed30C %>%   # call specific df !!! change to data_merged_seed34C <METADATA NEEDED FOR THIS!>
                                dplyr::filter(gain %in% loop.df_m[m,1])
for(i in 1:nrow(loop.df_i)){
  plate_id$flourescence <- as.numeric(plate_id$flourescence)
  plate_id$Treatment    <- 34 # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Age          <- "seed" # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Family       <- NA # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Type         <- NA # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Count        <- NA # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$gain         <- loop.df_m[m,1] # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  well.over.time        <- plate_id %>% 
                                dplyr::filter(Well %in% loop.df_i[i,1]) %>% 
                                dplyr::arrange(time) %>% 
                                dplyr::mutate(hours = as.numeric(difftime(time, 
                                                                          time[1], 
                                                                          units = "hours")),
                                              delta_florescence = flourescence - flourescence[1],
                                              AUC = pracma::trapz(
                                                                  hours, 
                                                                  flourescence)) %>% 
                                dplyr::select('Date', 'Treatment', 'PlateID', 'gain', 'Age', 'time', 'Family', 'hours',
                                              'Well', 'Type', 'Count', 'AUC', 'delta_florescence')
                      
  output.cumulative.df <- rbind(output.cumulative.df, 
                                well.over.time)
  
  running.df$Date      <- well.over.time$Date[1]
  running.df$Treatment <- well.over.time$Treatment[1]
  running.df$PlateID   <- well.over.time$PlateID[1]
  running.df$Age       <- well.over.time$Age[1]
  running.df$Well      <- well.over.time$Well[1]
  running.df$Family    <- well.over.time$Family[1]
  running.df$Type      <- well.over.time$Type[1]
  running.df$Count     <- well.over.time$Count[1]
  running.df$AUC       <- well.over.time$AUC[1]
  running.df$gain      <- well.over.time$gain[1]
  
   output.df <- rbind(output.df,
                     running.df) #bind to a cumulative list dataframe
   print(output.df) # print to monitor progress
   
   # mean blank AUC by each plate
  mean.AUC.blanks <- mean(
                           (output.df %>% dplyr::filter(Type %in% 'Blank'))$AUC
                          )
   
} # wells within plate end

}



ggplot(output.df, aes(x=Well, y=AUC))+ 
  geom_point() +
  facet_wrap(~gain)


output.df_WIDE <- reshape(output.df %>% select(-c("Family", "PlateID", "Age", "Type", "Count")),
                          idvar = c("Date","Treatment","Well"), timevar = "gain", direction = "wide")

output.df_WIDE$fudge <- (output.df_WIDE$AUC.70 - output.df_WIDE$AUC.65)

ggplot(output.df_WIDE, aes(x=AUC.65, y=AUC.70))+ 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") + # Adds trend line
  stat_regline_equation(label.x = 50000, label.y = 50000) +       # Adds slope equation
  stat_cor(aes(label = ..rr.label..), label.x = 50000, label.y = 40000) # Adds R2 value

```



Note: call specific df
  * loop.df_m and loop.df_i = columns in **rbind.df_seed34C**
  * plate_id == rows in **data_merged_seed34C** by common plate ID between **rbind.df_seed34C** 
```{r seed 34C auc calc function}

output.df   <- data.frame()
loop.df_m   <- data.frame(unique(rbind.df_seed34C$gain))  # call specific df
loop.df_i   <- data.frame(unique(rbind.df_seed34C$Well))  # call specific df

# Call the cumulative dataframe that we will write to in the for loop below
output.cumulative.df <- data.frame() # start dataframe 
output.cor.df        <- data.frame() # start dataframe 
output.cor.df_final  <- data.frame() # start dataframe 
running.df           <- data.frame(matrix(nrow = 1, ncol = 10)) # create dataframe to save cumunalitively during for loop
colnames(running.df) <- c('Date', 'Treatment', 'PlateID', 'Age', 'Well', 'Family', 'Type', 'Count', 'AUC', 'gain') # names for columns in the for loop

for(m in 1:nrow(loop.df_m)){
  plate_id      <- rbind.df_seed34C %>%   # call specific df !!! change to data_merged_seed34C <METADATA NEEDED FOR THIS!>
                                dplyr::filter(gain %in% loop.df_m[m,1])
for(i in 1:nrow(loop.df_i)){
  plate_id$flourescence <- as.numeric(plate_id$flourescence)
  plate_id$Treatment    <- 34 # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Age          <- "seed" # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Family       <- NA # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Type         <- NA # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$Count        <- NA # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  plate_id$gain         <- loop.df_m[m,1] # manually insert the temperature WAITING FOR METADATA TO CALL plate_id IN 'm'
  well.over.time        <- plate_id %>% 
                                dplyr::filter(Well %in% loop.df_i[i,1]) %>% 
                                dplyr::arrange(time) %>% 
                                dplyr::mutate(hours = as.numeric(difftime(time, 
                                                                          time[1], 
                                                                          units = "hours")),
                                              delta_florescence = flourescence - flourescence[1],
                                              AUC = pracma::trapz(
                                                                  hours, 
                                                                  flourescence)) %>% 
                                dplyr::select('Date', 'Treatment', 'PlateID', 'gain', 'Age', 'time', 'Family', 'hours',
                                              'Well', 'Type', 'Count', 'AUC', 'delta_florescence')
                      
  output.cumulative.df <- rbind(output.cumulative.df, 
                                well.over.time)
  
  running.df$Date      <- well.over.time$Date[1]
  running.df$Treatment <- well.over.time$Treatment[1]
  running.df$PlateID   <- well.over.time$PlateID[1]
  running.df$Age       <- well.over.time$Age[1]
  running.df$Well      <- well.over.time$Well[1]
  running.df$Family    <- well.over.time$Family[1]
  running.df$Type      <- well.over.time$Type[1]
  running.df$Count     <- well.over.time$Count[1]
  running.df$AUC       <- well.over.time$AUC[1]
  running.df$gain      <- well.over.time$gain[1]
  
   output.df <- rbind(output.df,
                     running.df) #bind to a cumulative list dataframe
   print(output.df) # print to monitor progress
   
   # mean blank AUC by each plate
  mean.AUC.blanks <- mean(
                           (output.df %>% dplyr::filter(Type %in% 'Blank'))$AUC
                          )
   
} # wells within plate end

}



ggplot(output.df, aes(x=Well, y=AUC))+ 
  geom_point() +
  facet_wrap(~gain)


output.df_WIDE <- reshape(output.df %>% select(-c("Family", "PlateID", "Age", "Type", "Count")),
                          idvar = c("Date","Treatment","Well"), timevar = "gain", direction = "wide")

output.df_WIDE$fudge <- (output.df_WIDE$AUC.65 - output.df_WIDE$AUC.60)

ggplot(output.df_WIDE, aes(x=AUC.60, y=AUC.65))+ 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") + # Adds trend line
  stat_regline_equation(label.x = 50000, label.y = 50000) +       # Adds slope equation
  stat_cor(aes(label = ..rr.label..), label.x = 50000, label.y = 40000) # Adds R2 value

```





```{r}
high_master_summ  <- Rmisc::summarySE(
                                data = (high_master %>% dplyr::filter(!Row %in% 'H')),
                                measurevar = "flourescence",
                                groupvars = c("column_id", "time" , "EBV_cat")
                             )

```

```{r}
blank_master_summ  <- Rmisc::summarySE(
                                data = (high_master %>% dplyr::filter(Row %in% 'H')),
                                measurevar = "flourescence",
                                groupvars = c("time")
                             )

```


```{r}
library(ggplot2)
ggplot(test, 
       aes(x = time, y = flourescence, group=Well)) +
  geom_point(size = 3) +
  geom_line()+
  geom_errorbar(aes(ymin = flourescence_cor - se, ymax = flourescence_cor + se),
                width = 0.15) +
  geom_smooth(method = "loess", se = FALSE) +
  theme_classic() # +
  # facet_wrap(~column_id)

```

```{r}
ggplot(blank_master_summ, 
       aes(x = time, y = flourescence)) +
  geom_point(size = 3) +
  geom_line()+
  geom_errorbar(aes(ymin = flourescence - se, ymax = flourescence + se),
                width = 0.15) +
  geom_smooth(method = "loess", se = FALSE) +

```